### 2025-07-17 paper/sections/experiments.qmd
not sure what the hell quarto is doing now

@@

```{=latex}
\begin{table*}
\input{tables/main.tex}
\end{table*}
```

Key performance metrics and bootstrapped standard errors (omitted if essentially zero) for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Actionability** (column 3): percentage reduction in costs with protected features. **Accuracy** (columns 4-7): test accuracies and robust accuracies ($\text{Acc}^*$) for CT and the baseline (BL). Counterfactual outcomes (col. 1-3) are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCo* at test time. Asterisks ($^*$) in columns 1-3 indicate that bootstrapped 99%-confidence interval of differences in mean outcomes does *not* include zero. Standard errors for accuracy (col. 4-7) are bootstrapped from the test set.
:::

>>>>

```{=latex}
\input{tables/main.tex}
```

Key counterfactual evaluation metrics and bootstrapped standard errors for all datasets. **Plausibility** (columns 1-2): percentage reduction in implausibility for $\text{IP}$ and $\text{IP}^*$, respectively; **Actionability** (column 3): percentage reduction in costs with protected features. Outcomes are aggregated across bootstrap samples and varying degrees of the energy penalty $\lambda_{\text{egy}}$ used for *ECCo* at test time. Asterisks ($^*$) indicate that bootstrapped 99%-confidence interval of differences in mean outcomes does *not* include zero.

:::

@@

![Test accuracies on adversarially perturbed data with varying perturbation sizes for all non-synthetic datasets.](paper/figures/acc.png){#fig-acc fig-env="figure*"}
